Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting

### 2021-01-09 paper/paper.tex
Change order of authors
Add new herding plot

\title{Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting}
\title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
\author{Daniel Ratke$^{2}$, Fabian Ritz$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
\mbox{}\\
$^1$Mobile and Distributed Systems Group, LMU Munich, Germany \\
$^2$LMU Munich, Germany \\
D.Ratke@campus.lmu.de} % email of corresponding author

@@

\begin{figure}%
    \centering
    \subfloat[][\centering Two predators and multiple prey]{\includegraphics[width=3.8cm]{figures/game_screen2.png} }%
    \subfloat[][\centering A stunned predator]{\includegraphics[width=3.66cm]{figures/stun_move2.png} }%
    \caption{The predator-prey environment, with yellow predators and blue prey. Predators can stun each other.}%
    \label{fig:aquarium}%
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{figures/Sterberisiko_vs_Herding_Two_Net_2.png}
\caption{TODO : Placeholder Chart (Idea: Three distributions with fish pop i10,i5,i2)}
\label{fig:herding}
\end{center}
\end{figure}

>>>>

\title{Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting}
\title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
\author{Fabian Ritz Ratke$^{1}$, Daniel Ratke$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
\mbox{}\\
$^1$Mobile and Distributed Systems Group, LMU Munich, Germany \\
$^2$LMU Munich, Germany \\
D.Ratke@campus.lmu.de} % email of corresponding author

@@

\begin{figure}%
    \centering
    \subfloat[][\centering Two predators and multiple prey]{\includegraphics[width=3.8cm]{figures/game_screen2.png} }%
    \subfloat[][\centering A stunned predator]{\includegraphics[width=3.66cm]{figures/stun_move2.png} }%
    \caption{The predator-prey environment, with yellow predators and blue prey. Predators can stun each other --- a stunned predator appears purple and cannot move for a certain number of steps.}%
    \label{fig:aquarium}%
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\textwidth]{figures/herding.png}
\caption{TODO}
\label{fig:herding}
\end{center}
\end{figure*}
